Total Score

### 2023-02-02 src/MSAtotal_scores.Rmd
rounded final scores and reordered columns

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

@@

```{r}
criteria_all <- real_estate_score_data %>% 
  inner_join(rental_policy_score_data)  %>% 
  inner_join(reopt_data) %>% 
  inner_join(climate_risk_data)
```

@@

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(total_score_students = cbsa, #this is just a place holder
         real_estate_score = as.numeric(real_estate_score),
         landlord_score = as.numeric(landlord_score)
  )

@@

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(score_climate50 = cbsa, #this is just a place holder
         real_estate_score = as.numeric(real_estate_score),
         landlord_score = as.numeric(landlord_score)
  )

@@

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(score_climate40 = cbsa, #this is just a place holder
         real_estate_score = as.numeric(real_estate_score),
         landlord_score = as.numeric(landlord_score)
  )

@@

```{r rename columns and output to google sheet}
criteria_all <- criteria_all %>% 
  rename(financial_score = normalized_irr,
         climate_impact = inverted_n_total_co2,
         health_impact = inverted_n_health_emissions_cost,
         electricity = normalized_annual_renewable,
         climate_risk = normalized_inverted_climate_risk)

sheet_write(criteria_all, ss = "https://docs.google.com/spreadsheets/d/1yqjhJvXUcEiC3qiYWkKNlF6NNpYXWg15zZHwmwpS5Q0/edit#gid=0")
```

```{r}
column_order <- c("real_estate_weighted", "rental_weighted", "financial_weighted", "electricity_weighted", "climate_impact_weighted", "climate_risk_weighted", "health_weighted", "cbsa", "city_msa", "state")

weighted_criteria <- criteria_all %>% 
  rename(real_estate_weighted = real_estate_score,
        rental_weighted = landlord_score,
        financial_weighted = normalized_irr,
        electricity_weighted = normalized_annual_renewable,
        climate_impact_weighted = inverted_n_total_co2,
        climate_risk_weighted = normalized_inverted_climate_risk,
        health_weighted = inverted_n_health_emissions_cost)

weighted_criteria <- weighted_criteria[, column_order]

@@

>>>>

```{r setup, include=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

@@

```{r read in data}
criteria_all <- real_estate_score_data %>% 
  inner_join(rental_policy_score_data)  %>% 
  inner_join(reopt_data) %>% 
  inner_join(climate_risk_data) # combine all criteria scores into one dataframe

# reorder columns
col_order <-c("cbsa", "city_msa", "state", "real_estate_score", "landlord_score", "normalized_annual_renewable", "normalized_irr", "inverted_n_total_co2", "normalized_inverted_climate_risk", "inverted_n_health_emissions_cost")

criteria_all <- criteria_all[, col_order]

@@

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(total_score_students = cbsa) #this is just a place holder

@@

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(score_climate50 = cbsa) #this is just a place holder

@@

#make landlord_score column
criteria_all <- criteria_all %>% 
  mutate(score_climate40 = cbsa) #this is just a place holder

@@

```{r rename columns and output to google sheet}

criteria_all <- criteria_all %>% 
  rename(financial_score = normalized_irr,
         climate_impact = inverted_n_total_co2,
         health_impact = inverted_n_health_emissions_cost,
         electricity = normalized_annual_renewable,
         climate_risk = normalized_inverted_climate_risk) %>% 
  mutate_if(is.numeric, ~round(., 5))

sheet_write(criteria_all, ss = "https://docs.google.com/spreadsheets/d/1yqjhJvXUcEiC3qiYWkKNlF6NNpYXWg15zZHwmwpS5Q0/edit#gid=0", sheet = "criteria_all")
```

@@

ggplot(data = score_tidy, aes(y = city_msa, x = total_score_owen, fill = criteria)) + 
    geom_col()
